Source Summaries

### 2020-01-31 sourceSummaries.tex
Don't know what I did but it compiles now
updated some styling and my reference
Fixed bibliography/table of contents interaction
Fixed uneven margins
Couple more formatting changes
Added Joshua\'s first source summary

\documentclass[a4paper,12pt]{article}
\begin{document}
    \title{Source Summaries}
    \author{Quintin Walters, Joshua Niemann, Connor Leavesley,\\
    Daniel Capps, Jacob Ruud}
    \date{\today}
    \maketitle
\break
\tableofcontents
\break

\break
\noindent
\section{Filizzola 2018 Security}
\subsection{Citation}

\noindent
@article\{filizzola2018security,

title=\{Security Analysis of Bluetooth Technology\},

author=\{Filizzola, Daniel and Fraser, Sean and Samsonau, Nikita\},

year=\{2018\},

organization=\{MIT\}

\noindent
\}

@@

>>>>

\documentclass[letterpaper,12pt]{article}
\usepackage{natbib}
\usepackage{bibentry}
\usepackage[hyphens]{url}
\usepackage[numbib]{tocbibind}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}

\bibliographystyle{plainnat}

\begin{document}
	\nobibliography*

    \title{Source Summaries}
    \author{Quintin Walters, Joshua Niemann, Connor Leavesley,\\
    Daniel Capps, Jacob Ruud}
    \date{\today}
    \maketitle
\break
\tableofcontents
\break

\noindent
\section{Filizzola 2018 Security}
\subsection{Citation}

\noindent

\Urlmuskip=0mu plus 1mu\relax
\bibentry{filizzola2018security}

@@

\Urlmuskip=0mu plus 1mu\relax

\pagebreak

\section{Extracting the Security Features Implemented in a Bluetooth LE Connection}

\noindent

\Urlmuskip=0mu plus 1mu\relax
\bibentry{8622000}

\noindent
The authors detail the encryption and authentication standards found in the Bluetooth Low Energy Protocol, from Bluetooth 4.0 to Bluetooth 5.0.  The researchers also look at several BLE devices to analyze their security models.
\subsection{Theory}

\noindent
The researchers found that many modern fitness trackers use older versions of Bluetooth low energy.  They also found that these fitness trackers often do not enable optional features that make bluetooth much more secure.  As a result, most of the encryption was trivial to decrypt.  The researchers then created an app that uses the Bluetooth sniff log functionality present in the developer section in Android to extract the security features of a bluetooth low energy device.

\noindent
The authors want to make their app much more usable to the average consumer.  Right now it's very oriented toward technical-minded researchers.

\bibliography{references}
